---
title: "Travaux Pratiques 2: Risk Management"
output:
  bookdown::html_document2:
  html_document:
 #  df_print: paged
 # pdf_document: default
---


```{r, echo = FALSE}

# Setting global options for the document
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(fig.align = "center")
opts_knit$set(eval.after = "fig.cap")

```
```{r}

# Include f_utils file that contains functions used later such as
# Black-Scholes pricer, rate interpolation, forward rate calculator, etc ...
source(here("Code", "Src", "f_utils.R"))

# Load market data
load(here("Data", "Original", "Market.rda"))

```


# Loading the data
The file **Market.rda** contains the list **Market**.

The first element of the list **Market** is an xts object corresponding to the 
value of the SP500 index from "2000-01-03" until "2013-09-10".

The second element vix corresponds to the value of the VIX  index at the same 
dates.

The third element rf corresponds to the term structure on "2013-09-10" for 14
maturities varying from 1 day to 30 years.
The term structure for the interest rates can be seen in 
Figure \@ref(fig:ratestructure) .
```{r ratestructure, fig.cap = my_caption }
my_caption = " Interest rates term structure."
x_plot = as.numeric(names(Market$rf) )
y_plot = 100 * as.numeric(Market$rf)
plot(x = x_plot , y = y_plot , type = "l", lwd = 2, col = "blue",
     xlab = "Maturities (years)", ylab = "Interest rates (%)")
points(x = x_plot, y = y_plot, col = "blue", pch = 16)
```

The fourth (calls) and the fifth (puts) contains the strikes (K), 
maturities (tau) and implied volatilities (IV) for calls and puts options 
respectively.

We plot the volatility surface in Figure \@ref(fig:surfvolputs) .


```{r surfvolputs, fig.cap = my_caption }
my_caption = " Volatility surface for the options in the list **Market**."
lib_vec = c("xts", "rgl", "akima", "knitr", "plotly")
invisible(lapply(lib_vec, f_install_load_lib)) # no output from lapply

# Volatility surface

obs_option = rbind(Market$puts, Market$calls)
#obs_option = Market$puts
strike_mkt = obs_option[, 1]
tau_mkt =  obs_option[, 2]
IV_mkt =  obs_option[, 3]


x = tau_mkt
y = strike_mkt
z = IV_mkt
n_interpolation = 500
# Use linear interpolation to create values for a surface plot
spline_interpolated = interp(x = x,
                             y = y,
                             z = z,
                             duplicate = "mean",
                             xo = seq(min(x), max(x), length = n_interpolation),
                             yo = seq(min(y), max(y), length = n_interpolation),
                             linear = TRUE, extrap = FALSE)

x.si = spline_interpolated$x
y.si = spline_interpolated$y
z.si = spline_interpolated$z

p = plot_ly(x = x.si, y = y.si, z = z.si, type = "surface") %>%
layout( scene = list( xaxis = list(title = "Maturities"),
                      yaxis = list(title = "Strikes"),
                      zaxis = list(title = "IV"),
                      camera = list(eye = list(x = 1.5, y = 1.5, z = 1.5) )
                      )
        )

# Print the plot
p 

```



```{r}

# Initializing recurrent variables

S0 = as.numeric(tail(Market$sp500, n = 1)) # Current index value
VIX = as.numeric(tail(Market$vix, n = 1)) # Current vix value

# Preparing the vectors
S_vec = rep(S0, 4)
K_vec = c(1600, 1650, 1750, 1800)
n_days_now = c(20, 20, 40, 40)
n_days_5d = c(15, 15 , 35, 35)
TT_vec_now = n_days_now / 250.0
TT_vec_5d = n_days_5d / 250.0
vol_vec = rep(VIX, 4)
isCall_vec = rep(TRUE, 4)

# rates at 20 and 40 days
r5 = f_rf_interpolate(t1 = 5.0 / 360., rf = Market$rf)
r20 = f_rf_interpolate(t1 = 20.0 / 360., rf = Market$rf)
r40 = f_rf_interpolate(t1 = 40.0 / 360., rf = Market$rf)
r_vec_now = c(r20, r20, r40, r40)

# Forward rates between (5 and 20 days) and (5 and 40 days)
fwd_5_20 = f_fwd_rate(t1 = 5. / 360.,
                      t2 = 20. / 360.,
                      rf = Market$rf)
fwd_5_40 = f_fwd_rate(t1 = 5. / 360.,
                      t2 = 40. / 360.,
                      rf = Market$rf)

r_vec_5d = c(fwd_5_20, fwd_5_20, fwd_5_40, fwd_5_40)

# mean, variance of sp500 and vix log-returns
n_sim = 10000L
lib_vec = c("PerformanceAnalytics")
invisible(lapply(lib_vec, f_install_load_lib))

# log-returns
sp500_logrets = PerformanceAnalytics::Return.calculate(Market$sp500,
                                                       method = "log")
sp500_logrets = sp500_logrets[-1] # Get rid of the first line
vix_logrets = PerformanceAnalytics::Return.calculate(Market$vix,
                                                     method = "log")
vix_logrets = vix_logrets[-1]
mu_sp500 = mean(sp500_logrets)
mu_vix = mean(vix_logrets)
# Finding mean and variance
sigma2_sp500 = (length(sp500_logrets) - 1) / (length(sp500_logrets)) *
  var(sp500_logrets)
sigma2_vix = (length(vix_logrets) - 1) / (length(vix_logrets)) *
  var(vix_logrets)

```
# Pricing of a portfolio of options

```{r}

price_vec = f_vBS_price(S_vec,
                        K_vec,
                        TT_vec_now,
                        vol_vec,
                        r_vec_now,
                        isCall_vec)
V0 = sum(price_vec)
options_df = data.frame(
  "S0" = S_vec,
  "K" = K_vec,
  "tau" = TT_vec_now,
  "sigma" = vol_vec,
  "r" = round(r_vec_now, 6),
  "C" = round(price_vec, 3)
)

```

The prices of the call options using the Black-Scholes formula are given in 
table \@ref(tab:bookCalls) .

```{r}

knitr::kable(options_df, caption = "Prices of the (call) options in our book",
             label = "bookCalls" )

```

The price of this book (the sum of prices of the calls that constitutes 
the book) is $V_0$ = `r round(V0, 2)`.

# One risk driver and Gaussian model

In this section, we assume that the risk of our book of options is driven by 
a single factor namely the change in price of the SP500 index.
The log-returns of the index are assumed to follow a normal distribution with 
parameters given by the mean and standard deviation from the historical values.

```{r gauss1D, fig.cap = my_caption}

set.seed(2019)
# Generate n_sim new stock prices scenario
gauss_rets_sp500 = rowSums(matrix(
  rnorm(5 * n_sim, mean = mu_sp500,
        sd = sqrt(sigma2_sp500)),
  nrow = n_sim,
  ncol = 5
))
sp500_5d = S0 * exp(gauss_rets_sp500)

# profit and loss distribution for 1 risk driver (1D)
BV_5d = rep(NA, n_sim) # new book value

for (i in 1:n_sim) {
  S_vec = rep(as.numeric(sp500_5d[i]), 4)
  price_vec = f_vBS_price(S_vec,
                          K_vec,
                          TT_vec_5d,
                          vol_vec,
                          r_vec_5d,
                          isCall_vec)
  BV_5d[i] = sum(price_vec)
}
PL_gauss1D = exp(-5/360 * r5) * BV_5d - V0
VaR95_gauss1D = quantile(PL_gauss1D, 0.05)
ES95_gauss1D = mean(PL_gauss1D[PL_gauss1D <= VaR95_gauss1D])

f_hist(
  data = PL_gauss1D,
  threshold = VaR95_gauss1D,
  xlab = "PL_gauss1D"
)

my_caption = paste("P&L distribution for normal log-returns of the SP500.",
                   "The red line at", round(VaR95_gauss1D, 2),
                   "is the value at risk at 95% probability.")

```

We model `r n_sim` possible values for the stocks in 5 days and 
use them to estimate the distribution for the P&L in a week (5 days).
The distribution of the P\&L is given in Figure \@ref(fig:gauss1D) .

The VaR at risk at the 95% confidence level is
VaR95 = `r round(VaR95_gauss1D, 2)`
and the expected shortfall is ES95 = `r round(ES95_gauss1D, 2)`.
So we expect the book of options to lose at least 
`r round(abs(VaR95_gauss1D), 2)` from its initial value 5% of the time.  

# Two risk drivers and Gaussian model

In this section, we assume that the risk of our book of options is driven by 
two factors namely the change in price of the SP500 index and the volatility 
of the market (given by the VIX).
The log-returns of the SP500 and the VIX are assumed to follow a normal distribution with parameters given by the mean and standard deviation from the historical 
values.

```{r gauss2D, fig.cap = my_caption}

set.seed(2019)
lib_vec = c("mnormt")
invisible(lapply(lib_vec, f_install_load_lib))

# Gaussian model (MLE)
rets = cbind(sp500_logrets, vix_logrets)
n <- nrow(rets)
mu_gauss_biv <- colMeans(rets)
Sigma_gauss_biv <- ((n - 1) / n) * cov(rets)

M1 <- list(mu = mu_gauss_biv, Sigma = Sigma_gauss_biv)

tmp_biv = rmnorm(n = 5 * n_sim,
                 mean = M1$mu,
                 varcov = M1$Sigma)

# Generate n_sim new stock prices scenario
gauss_rets_sp500 = rowSums(matrix(tmp_biv[, 1], nrow = n_sim, ncol = 5))
gauss_rets_vix =  rowSums(matrix(tmp_biv[, 2], nrow = n_sim, ncol = 5))
sp500_5d = S0 * exp(gauss_rets_sp500)
vix_5d = VIX * exp(gauss_rets_vix)

# profit and loss distribution for 1 risk driver (1D)
BV_5d = rep(NA, n_sim) # new book value

r_vec = c(fwd_5_20, fwd_5_20, fwd_5_40, fwd_5_40)
for (i in 1:n_sim) {
  S_vec = rep(sp500_5d[i], 4)
  vol_vec = rep(vix_5d[i], 4)
  price_vec = f_vBS_price(S_vec,
                          K_vec,
                          TT_vec_5d,
                          vol_vec,
                          r_vec,
                          isCall_vec)
  BV_5d[i] = sum(price_vec)
}
PL_gauss2D = exp(-5/360 * r5) * BV_5d - V0
VaR95_gauss2D = quantile(PL_gauss2D, 0.05)
ES95_gauss2D = mean(PL_gauss2D[PL_gauss2D <= VaR95_gauss2D])

f_hist(
  data = PL_gauss2D,
  threshold = VaR95_gauss2D,
  xlab = "PL_gauss2D"
)

my_caption = paste("P&L distribution when log-returns of SP500 and VIX are
                   assumed to follow a bivariate normal distribution.
                   The red line at", round(VaR95_gauss2D, 2),
                   "represents the value at risk at 95% probability.")

```
We model `r n_sim` possible values for the SP500 and the VIX in 5 days and 
use them to estimate the distribution for the P&L in a week (5 days).
The distribution of the P\&L is given in Figure \@ref(fig:gauss2D) .

The VaR at risk at the 95% confidence level is
VaR95 = `r round(VaR95_gauss2D, 2)`
and the expected shortfall is ES95 = `r round(ES95_gauss2D, 2)`.
So we expect the book of options to lose at least 
`r round(abs(VaR95_gauss2D), 2)` from its initial value 5% of the time.

# Two risk drivers and copula-marginal model (Student-t and Gaussian copula)

In this section, we assume that the risk of our book of options is driven by 
two factors namely the change in price of the SP500 index and the volatility 
of the market (given by the VIX).
The log-returns of the SP500 are assumed to follow a Student-t distribution with 
$\nu = 10$ degrees of freedom and the log-returns of the VIX are assumed to
follow  a Student-t distribution with  $\nu = 5$ degrees of freedom.
A normal Copula is assumed to merge the marginals.

```{r ststgauss2D, fig.cap = my_caption }

set.seed(2019)
n_sim = 10000L
lib_vec = c("PerformanceAnalytics", "copula", "MASS", "fGarch")
invisible(lapply(lib_vec, f_install_load_lib))

df_sp500 = 10L
df_vix = 5L

# Fit student-t distributions
fit_sp500 =  suppressWarnings(fitdistr(sp500_logrets, "t", df = df_sp500))
fit_vix =  suppressWarnings(fitdistr(vix_logrets, "t", df = df_vix))

# Finding location and scale parameters of student-t distribution
mu_sp500 = as.numeric(fit_sp500$estimate[1])
mu_vix = as.numeric(fit_vix$estimate[1])

scale_sp500 = as.numeric(fit_sp500$estimate[2])
scale_vix = as.numeric(fit_vix$estimate[2])

# Merging using a normal Copula

U_sp500 = pstd(sp500_logrets,
               mean = mu_sp500,
               sd = scale_sp500,
               nu = df_sp500)
U_vix = pstd(vix_logrets,
             mean = mu_vix,
             sd = scale_vix,
             nu = df_vix)
U = cbind(as.numeric(U_sp500), as.numeric(U_vix))

C = normalCopula(dim = 2)

fit = fitCopula(C, data = U, method = "ml")

# Generating 5 days returns with the required relationship
U_sim = rCopula(5 * n_sim, fit@copula)
logrets_sp500 = rowSums(matrix(
  qstd(
    U_sim[, 1],
    mean = mu_sp500,
    sd = scale_sp500,
    nu = df_sp500
  ),
  nrow = n_sim,
  ncol = 5
))
logrets_vix  = rowSums(matrix(
  qstd(
    U_sim[, 2],
    mean = mu_vix,
    sd = scale_vix,
    nu = df_vix
  ),
  nrow = n_sim,
  ncol = 5
))


sp500_5d = S0 * exp(logrets_sp500)
vix_5d = VIX * exp(logrets_vix)

# profit and loss distribution for 1 risk driver (1D)
BV_5d = rep(NA, n_sim) # new book value

for (i in 1:n_sim) {
  S_vec = rep(sp500_5d[i], 4)
  vol_vec = rep(vix_5d[i], 4)
  price_vec = f_vBS_price(S_vec,
                         K_vec,
                         TT_vec_5d,
                         vol_vec,
                         r_vec_5d,
                         isCall_vec)
  BV_5d[i] = sum(price_vec)
}
PL_ststgauss2D = exp(-5/360 * r5) * BV_5d - V0
VaR95_ststgauss2D = quantile(PL_ststgauss2D, 0.05)
ES95_ststgauss2D = mean(PL_ststgauss2D[PL_ststgauss2D <= VaR95_ststgauss2D])

main_title =
  f_hist(
    data = PL_ststgauss2D,
    threshold = VaR95_ststgauss2D,
    xlab = "PL_ststgauss2D"
  )

my_caption = paste("P&L distribution when log-returns of the SP500 and 
                   the VIX are assumed to have Student-t marginals and their
                   marginals to be linked by a Gaussian copula . 
                   The red line at ", round(VaR95_ststgauss2D, 2), 
                   " represents the value at risk at 95% probability.")
```
We model `r n_sim` possible values for the SP500 and the VIX in 5 days and 
use them to estimate the distribution for the P&L in a week (5 days).
The distribution of the P\&L is given in Figure \@ref(fig:ststgauss2D) .

The VaR at risk at the 95% confidence level is
VaR95 = `r round(VaR95_ststgauss2D, 2)`
and the expected shortfall is ES95 = `r round(ES95_ststgauss2D, 2)`.
So we expect the book of options to lose at least 
`r round(abs(VaR95_ststgauss2D), 2)` from its initial value 5% of the time.


# Volatility surface

```{r volsurf, fig.cap = my_caption }

set.seed(2019)
lib_vec = c("mnormt")
invisible(lapply(lib_vec, f_install_load_lib))

f_parametric_IV = function(params, m, tau) {
  alpha1 = params[1]
  alpha2 = params[2]
  alpha3 = params[3]
  alpha4 = params[4]
  
  stopifnot(length(m) == length(tau)) #Check moneyness and tau have same length
  sigma = alpha1 + alpha2 * (m - 1) ** 2 + alpha3 * (m - 1) ** 3 +
    alpha4 * sqrt(tau)
  return(sigma)
}

f_obj_fn = function(params, options_data) {
  m_vec = options_data[, 1]
  tau_vec = options_data[, 3]
  IV_vec = options_data[, 4]
  sigma_model = f_parametric_IV(params, m_vec, tau_vec)
  return(sum(abs(sigma_model - IV_vec)))
}


calls_info = Market$calls
puts_info = Market$puts
options_all = rbind(calls_info, puts_info)
moneyness = options_all[, 1] / S0
options_all = cbind(moneyness, options_all)

# Gaussian model (MLE)
rets = cbind(sp500_logrets, vix_logrets)
n <- nrow(rets)
mu_gauss_biv <- colMeans(rets)
Sigma_gauss_biv <- ((n - 1) / n) * cov(rets)
M1 <- list(mu = mu_gauss_biv, Sigma = Sigma_gauss_biv)

tmp_biv = rmnorm(n = 5 * n_sim,
                 mean = M1$mu,
                 varcov = M1$Sigma)

# Generate n_sim new stock prices scenario
gauss_rets_sp500 = rowSums(matrix(tmp_biv[, 1], nrow = n_sim, ncol = 5))
gauss_rets_vix =  rowSums(matrix(tmp_biv[, 2], nrow = n_sim, ncol = 5))
sp500_5d = S0 * exp(gauss_rets_sp500)
vix_5d = VIX * exp(gauss_rets_vix)

# Solving for parameters alpha1, alpha2, alpha3 and alpha4
params_vec = rep(0, 4)
obj_min = 1e6
n_repeat = 100

for (i in 1:n_repeat) {
  ini_params = runif(4, min = -5, max = 5)
  fit_params = optim(par = ini_params, f_obj_fn,
                     options_data = options_all)
  if (fit_params$value < obj_min) {
    obj_min = fit_params$value
    params_vec = fit_params$par
  }
}


#repricing the portfolio

#  Shift parameter
delta_shift = params_vec[1] + params_vec[4] - VIX


#  Volatility in 5 days
vix_shift = vix_5d + delta_shift


BV_new = rep(NA, n_sim) # new book value
for (i in 1:n_sim) {
  S_vec = rep(sp500_5d[i], 4)
  vol_vec = rep(vix_shift[i], 4)
  price_vec = f_vBS_price(S_vec,
                         K_vec,
                         TT_vec_5d,
                         vol_vec,
                         r_vec_5d,
                         isCall_vec)
  BV_new[i] = sum(price_vec)
}
PL_gauss_volsurf = exp(-5/360 * r5) * BV_new - V0
VaR95_gauss_volsurf = quantile(PL_gauss_volsurf, 0.05)
ES95_gauss_volsurf = mean(PL_gauss_volsurf[PL_gauss_volsurf <= VaR95_gauss_volsurf])

f_hist(
  data = PL_gauss_volsurf,
  threshold = VaR95_gauss_volsurf,
  xlab = "PL_gauss_volsurf"
)

my_caption = paste("P&L distribution when log-returns of the SP500 and the 
                   VIX are assumed to follow a bivariate normal distribution. 
                   The simulated values of the VIX are shifted by the one year
                   ATM volatility difference. The red line at ", 
                   round(VaR95_gauss_volsurf, 2), 
                   " represents the value at risk at 95% probability.")

```

We model `r n_sim` possible values for the SP500 and the VIX in 5 days and 
use them to estimate the distribution for the P&L in a week (5 days).
The simulated values of the VIX are then shifted by the difference between the
one year ATM value of the implied volatility and today value of the VIX.
The distribution of the P\&L is given in Figure \@ref(fig:volsurf) .


The VaR at risk at the 95% confidence level is
VaR95 = `r round(VaR95_gauss_volsurf, 2)`
and the expected shortfall is ES95 = `r round(ES95_gauss_volsurf, 2)`.
So we expect the book of options to lose at least 
`r round(abs(VaR95_gauss_volsurf), 2)` from its initial value 5% of the time.

# Full approach

```{r full, fig.cap = my_caption}

set.seed(2019)
n_sim = 10000L
lib_vec = c("PerformanceAnalytics", "copula", "MASS", "fGarch", "rugarch")
invisible(lapply(lib_vec, f_install_load_lib))

# log returns
mu_sp500 =  mean(sp500_logrets)
mu_vix = mean(vix_logrets)

## Fit GARCH(1,1) to log returns of SP500
fit_GARCH_sp500.spec = ugarchspec(
  variance.model = list(model = "sGARCH",
                        garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(0, 0),
                    include.mean = FALSE),
  distribution.model = "norm"
)
fit_GARCH_sp500   =  ugarchfit(data = sp500_logrets,
                               spec = fit_GARCH_sp500.spec)

# MLE
mu_res_sp500 = mean(as.numeric(fit_GARCH_sp500@fit$z))
sd_res_sp500 = sd(as.numeric(fit_GARCH_sp500@fit$z)) *
  sqrt((length(sp500_logrets) - 1) / length(sp500_logrets))


# Fit AR(1) to log returns of Vix
fit_vix = arima(x = vix_logrets, order = c(1, 0, 0))
mu_res_vix = mean(fit_vix$residuals)
sd_res_vix =  sqrt((length(sp500_logrets) - 1) / length(sp500_logrets)) *
  sd(fit_vix$residuals)

# Distribution of the marginals
U1 = pnorm(fit_GARCH_sp500@fit$z, mean = mu_res_sp500, sd = sd_res_sp500)
U2 = pnorm(fit_vix$residuals , mean = mu_res_vix, sd = sd_res_vix)
U = cbind(U1, U2)

# Fit normal copula
C = normalCopula(dim = 2)
fit = fitCopula(C, data = U, method = "ml")

# Generate draws for the invariants
U_sim = rCopula(5 * n_sim, fit@copula)
res_sp500 = matrix(
  qnorm(U_sim[, 1],  mean = mu_res_sp500, sd = sd_res_sp500),
  nrow = n_sim,
  ncol = 5
)
res_vix = matrix(qnorm(U_sim[, 2],  mean = mu_res_vix, sd = sd_res_vix),
                 nrow = n_sim,
                 ncol = 5)

# Initializing the GARCH(1,1) process
logrets_sp500 = matrix(NA, nrow = n_sim, ncol = 6)
logrets_sp500[, 1] = rep(tail(sp500_logrets, 1), n_sim)
sigma2_sp500 = rep(tail(fit_GARCH_sp500@fit$sigma, 1) ^ 2, n_sim)

# Initializing the AR(1) process
logrets_vix = matrix(NA, nrow = n_sim, ncol = 6)
logrets_vix[, 1] = rep(tail(vix_logrets, 1), n_sim)


for (i in 1:5) {
  logrets_vix[, i + 1] = as.numeric(fit_vix$coef["intercept"]) +
    as.numeric(fit_vix$coef["ar1"]) * logrets_vix[, i]  +
    res_vix[, i]
  
  sigma2_sp500 = as.numeric(fit_GARCH_sp500@fit$coef["omega"]) +
    as.numeric(fit_GARCH_sp500@fit$coef["alpha1"]) * logrets_sp500[, i] ^
    2 +
    as.numeric(fit_GARCH_sp500@fit$coef["beta1"]) * sigma2_sp500
  
  logrets_sp500[, i + 1] = res_sp500[, i] *
    sigma2_sp500 ^ 0.5
}

sp500_new = S0 * exp(rowSums(logrets_sp500[, 2:ncol(logrets_sp500)]))
vix_5d = VIX * exp(rowSums(logrets_vix[, 2:ncol(logrets_vix)]))


# profit and loss distribution for 1 risk driver (1D)
BV_new = rep(NA, n_sim) # new book value

for (i in 1:n_sim) {
  S_vec = rep(sp500_new[i], 4)
  vol_vec = rep(vix_5d[i], 4)
  price_vec = f_vBS_price(S_vec,
                          K_vec,
                          TT_vec_5d,
                          vol_vec,
                          r_vec_5d,
                          isCall_vec)
  BV_new[i] = sum(price_vec)
}
PL_full = exp(-5/360 * r5) * BV_new - V0
VaR95_full = quantile(PL_full, 0.05)
ES95_full = mean(PL_full[PL_full <= VaR95_full])

f_hist(
  data = PL_full,
  threshold = VaR95_full,
  xlab = "PL_full_approach"
)

my_caption = paste("P&L distribution when log-returns of the SP500 follow 
                   an ARMA(1,1) and the log-returns of the VIX an AR(1). 
                   The invariants of the two processes are linked by a 
                   Gaussian copula.  The red line at ", 
                   round(VaR95_full, 2), 
                   " represents the value at risk at 95% probability.")

```

Here, we fit a GARCH(1,1) to the log-returns of the SP500 and an AR(1) process 
to the log-returns of the VIX. The residuals of the two processes are 
assumed to be invariants and to be linked by a Gaussian copula.
We generate `r n_sim` possible values for the SP500 and the VIX in 5 days and 
use them to estimate the distribution for the P&L in a week (5 days).
The distribution of the P\&L is given in Figure \@ref(fig:full) .


The VaR at risk at the 95% confidence level is
VaR95 = `r round(VaR95_full, 2)`
and the expected shortfall is ES95 = `r round(ES95_full, 2)`.
So we expect the book of options to lose at least 
`r round(abs(VaR95_full), 2)` from its initial value 5% of the time.
